MP MetaAnalysis

### 2018-09-19 Paper_Analyses.Rmd
updated Methods/Results

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(wesanderson)

@@

```{r ReadIn,  echo = FALSE}
#Get the data
source("scripts/calculateES.R")

@@

# Plotting defaults

```{r PlotAPATheme}
#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

# Descriptive data

The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.

The next table shows what type of publications were included in our meta-analysis
```{r DescriptivesPubtype, echo = FALSE}

@@

@@

## Type of data on which we calculated effect sizes
The table below shows based on which data we calculated effect sizes.

```{r DescriptivesES, echo = FALSE}
#how did we calculate effect sizes?

@@

## Number of unique infants

```{r DescriptivesInfnum, echo = FALSE}

infnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "n_1")]
infnum_info <- unique(infnum_info)

number_of_infants <- sum(infnum_info$n_1)

@@

The database contains data from `r number_of_infants` unique infants.

## Number of unique experimental conditions

```{r DescriptivesExpCond, echo = FALSE}

condnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
condnum_info <- unique(condnum_info)

number_of_cond <- nrow(condnum_info)

@@

The database contains data from `r number_of_cond` unique experimental conditions

## Type of comparison of the time-course data calculated
We also have different ways of comparison of the time-course data, as the next table shows.

kable(comparison_info)
#table(db_ET_MP$es_method)
```

## Type of distractor
This is a summary of the type of distractor used in an experiment

```{r DescriptivesDISTRACT, echo = FALSE}
#What kind of distractor was used?

distr_info <- distract_dat %>%
  group_by(object_pair) %>%
  summarize(count = n())

kable(distr_info)

@@

## Whether word was pronounced both correctly as well as mispronounced
This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment

```{r DescriptivesCoMp, echo = FALSE}
#What kind of distractor was used?

mix_info <- mix_co_mp %>%
  group_by(word_correct_and_MP) %>%
  summarize(count = n())

kable(mix_info)

@@

## Size of analysis time window

Where possible, we noted the time window for analysis. First, let's look at the offset (in milliseconds) after the start of the word, i.e. the begin of a give analysis window for a naming effect

```{r TimeWindowOffset}
offset_info <- time_wind_dat %>%
  group_by(offset) %>%
  summarize(count = n())

kable(offset_info)

@@

## Duration of post naming window
Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.

```{r TimeWindowduration}
duration_info <- db_ET_correct %>%
  group_by(post_nam_dur) %>%
  summarize(count = n())

kable(duration_info)

@@

In summary, we see little consistency in analysis methods of comparable studies looking at naming and mispronunciation effects.

## Mispronunciation Sensitivity in the youngest ages
Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity

```{r YoungAge, echo = FALSE}
youngest <- subset(dat, min_age_1 < 365)

unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()

@@

# Meta-Analysis

## Main Mispronunciation Sensitivity Effects

### Correct object identification effect

@@

summary(rma_correct)

#kable(round(coef(summary(rma_correct)), 2))

@@

### Mispronunciation object identification effect

@@

summary(rma_MP)

@@

### Mispronunciation Sensitivity effect

```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

summary(rma_MPeffect)

rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)

summary(rma_MPeffect_1)

@@

## Main Mispronunciation Sensitivity Effects with Age Moderators

### Correct object identification effect with age moderator

@@

summary(rma_correct_age)
#kable(round(coef(summary(rma_correct_age)), 2))

@@

### Mispronunciation object identification effect with age moderator

@@

summary(rma_MP_age)
```

### Mispronunciation Sensitivity effect with age moderator

```{r MPEffect_age}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

summary(rma_MPeffect_age)

@@

## Plotting Mispronunciation Effect

### Plot Mispronunciation Effect by Age (color)

```{r PlotMPEffect}

@@

min(dat$mean_age_1/30.44)
max(dat$mean_age_1/30.44)

@@

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 600, height = 400, units = "px")

@@

### Plot Mispronunciation Effect by Age (bw)

```{r PlotMPEffect_BW}

>>>>

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)

# set Table count at 0
t_num <- 0

# set Figure count at 0
f_num <- 0

r2 <- function(x){ round(x, 2)}

psig <- function(x){
  ifelse(x < .0001, "< .0001",
         ifelse(x < .001, "< .001",
                ifelse(x < .01, "< .01",
                       ifelse(x > .01 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))))
}

@@

```{r ReadIn,  echo = FALSE}

#Get the effect size data
source("scripts/calculateES.R")

@@

Plotting defaults

```{r PlotAPATheme, echo = FALSE}
#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

# Methods

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014). In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials. (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).

## Study Selection
We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We screened the 398 items, removing 99 duplicate items. We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech. The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

```{r DescriptivesPubtype, echo = FALSE}

t_num <- t_num+1

@@

pi <- dat[,c("short_cite", "publication_status")]
pi <- unique(pi)

c.plot <- ggplot(pi, aes(x= publication_status)) + 
  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
  geom_bar(stat="count")+
  coord_cartesian(ylim = c(0, 30))+
  apatheme+
  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
        axis.title.x = element_blank())

c.plot

  jpeg(filename = "figures/Pub_count.jpg", 
       width = 500, height = 500, units = "px")

  c.plot

@@

## Data Entry

The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., in press). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics: 
1 Condition: Were words mispronounced or not;
2 Mean age reported per group of infants, in days;
3 Vocabulary size:  
4 Size of mispronunciation, measured in features changed;
5 Distractor familiarity: familiar, unfamiliar;
6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
7 Position of mispronunciation: onset, medial, offset;
8 Type of mispronunciation: consonant, vowel;

We separated out conditions according to whether or not the target word was mispronounced to be able to investigate both infants' looking to the target picture separated by whether or not words were mispronounced and their mispronunciation sensitivity, which is the difference between looking in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).  The fact that the same infants have contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(dat)` records in our data.

## Data analysis

kable(comparison_info)
#table(db_ET_MP$es_method)
```
```{r DescriptivesES, echo = FALSE}
#how did we calculate effect sizes?

@@

All scripts and raw data are available on Open Science Framework (OSF). INSERT LINK AS FOOTNOTE HERE. Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper. Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for the pre-naming phase from the PTL score for the post-naming phase. When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced). Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with chance (50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`)). For these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.

We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (mispronunciation sensitivity). The effect size we report in the present paper are based on comparison of means, standardized by their variance. The most well-known effect size from this group is Cohen's *d* (Cite cohen). To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).

No authors made their raw data available. Instead, we calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. One paper reported this correlation, while we were able to compute correlations using means, standard deviations, and t-values (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, submitted). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We computed a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R (R citation) package metafor (Viechtbauer, 20XX, Multulevel reference). This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.

## Publication Bias

In the psychological sciences, there is a documented reluctance to publish null results. As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012). To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests. We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R (R Core Team, 2016) package metafor (Viechtbauer, 2010). Effect szes with low-variance are closer to the estimated mean, while effect sizes with high-variance show an increased, evenly-distributed spread around the estimated mean. Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; Simonsohn, Simmons, & Nelson, 2014). This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices. Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.

## Meta-analysis

The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R (R Core Team, 2016) package metafor
(Viechtbauer, 2010). To investigate how development impacts mispronunciation sensitivity, our core theoretical investigation, we introduce age (centered; in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model. For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).

# Results

## Publication Bias

```{r FunnelPlotAsymm_correct, echo = FALSE}

rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
# Publication bias can become visible in funnel plot asymmetry. 
# Metafor comes with several options to check this, I chose ranktest and regtest
# correct object identification
rmac <- ranktest(rma_correct)
#rmac

@@

```{r FunnelPlotAsymm_misp, echo=FALSE}

# mispronounced object identification
rmam <- ranktest(rma_MP)
#rmam
```

Figure 1 plots the funnel plots for object identification for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016). Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`). These results, in conjunction with the assymmetric funnel plot (Figure 1) indicate bias in the literature. This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e. smaller variance) than expected (top left, outside the triangle).

```{r FunnelPrep, echo = FALSE}
### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

#Themes and plot
funnel_theme=theme_bw()+
  theme(#panel.grid.major=element_blank(),
    #panel.grid.minor=element_blank(),
    #panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=22),
    legend.position='none')

@@

```{r FunnelCorrect, echo = FALSE}

#Rename a bunch of things for ease
dat_co = db_ET_correct
#dat_co=db_ET_correct
dat_co <-
  dat_co %>% 
  rename(cite = short_cite,
         yi = g_calc,
         vi = g_var_calc)

#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order

dat_co <-
  dat_co %>% 
  select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
  arrange(desc(yi))

#Get standard errors from variances
dat_co$se = sqrt(dat_co$vi)

#Calculate 95% CI values
dat_co$lowerci = (-1.96*dat_co$se)+dat_co$yi
dat_co$upperci = (1.96*dat_co$se)+dat_co$yi

#Store the meta-analytic estimate and its standard error from whatever model you run
#summary(rma_correct)
estimate_co = coef(summary(rma_correct))$estimate
se_co = coef(summary(rma_correct))$se

#Store a vector of values that spans the range from 0
#to the max value of impression (standard error) in your dataset.
#Make the increment (the final value) small enough (I choose 0.001)
#to ensure your whole range of data is captured
se.seq_co=seq(0, max(dat_co$se), 0.001)

#Now, compute vectors of the lower-limit and upper limit values for
#the 95% CI region, using the range of SE that you generated in the previous step, 
#and the stored value of your meta-analytic estimate.
ll95_co = estimate_co-(1.96*se.seq_co)
ul95_co = estimate_co+(1.96*se.seq_co)

#You can do this for a 99% CI region too
ll99_co = estimate_co-(3.29*se.seq_co)
ul99_co = estimate_co+(3.29*se.seq_co)

#And finally, do the same thing except now calculating the confidence interval
#for your meta-analytic estimate based on the stored value of its standard error
meanll95_co = estimate_co-(1.96*se_co)
meanul95_co = estimate_co+(1.96*se_co)

#Now, smash all of those calculated values into one data frame (called 'dfCI').
#You might get a warning about '...row names were found from a short variable...'
#You can ignore it.
dfCI_co = data.frame(ll95_co, ul95_co, ll99_co,
                  ul99_co, se.seq_co, estimate_co, meanll95_co, meanul95_co)

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
  #Regression line for the FP asymmetry
  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
  #Add your data-points to the scatterplot
  geom_point(size = 2.5, colour="black") +
  #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
  # give it a title
    ggtitle("Correct") +
    # make sure both plots have same scale
    # still ylim because we haven't flipped yet
    #coord_cartesian(ylim = c(0.5, 0))+
  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
  #to the lower and upper limits of your 95% CI region
  #And dashed lines corresponding to your 99% CI region
  #Add lines corresponding to 0 and estimate
  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
  #at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
  #Specify the range and interval for the tick-marks of the y-axis (Zr);
  #Choose values that work for you based on your data
  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
  #And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
  #Finally, apply my APA-format theme (see code at end of post).
  #You could, alternatively, specify theme_bw() instead.
  funnel_theme

#Call the pretty funnel plot
#fp_co
#ggsave("figures/FunnelPlot_correct.pdf")

@@

```{r FunnelMisp, echo = FALSE}

  #Rename a bunch of things for ease
dat_mp = db_ET_MP  
#dat_mp=db_ET_MP
  dat_mp <-
    dat_mp %>% 
    rename(cite = short_cite,
           yi = g_calc,
           vi = g_var_calc)

  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order

  dat_mp <-
    dat_mp %>% 
    select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
    arrange(desc(yi))

  #Get standard errors from variances
  dat_mp$se = sqrt(dat_mp$vi)

  #Calculate 95% CI values
  dat_mp$lowerci = (-1.96*dat_mp$se)+dat_mp$yi
  dat_mp$upperci = (1.96*dat_mp$se)+dat_mp$yi

  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
  #summary(rma_MP)
  estimate_mp = coef(summary(rma_MP))$estimate
  se_mp = coef(summary(rma_MP))$se

  #Store a vector of values that spans the range from 0
  #to the max value of impression (standard error) in your dataset.
  #Make the increment (the final value) small enough (I choose 0.001)
  #to ensure your whole range of data is captured
  se.seq_mp=seq(0, max(dat_mp$se), 0.001)

  #Now, compute vectors of the lower-limit and upper limit values for
  #the 95% CI region, using the range of SE that you generated in the previous step, 
  #and the stored value of your meta-analytic estimate.
  ll95_mp = estimate_mp-(1.96*se.seq_mp)
  ul95_mp = estimate_mp+(1.96*se.seq_mp)

  #You can do this for a 99% CI region too
  ll99_mp = estimate_mp-(3.29*se.seq_mp)
  ul99_mp = estimate_mp+(3.29*se.seq_mp)

  #And finally, do the same thing except now calculating the confidence interval
  #for your meta-analytic estimate based on the stored value of its standard error
  meanll95_mp = estimate_mp-(1.96*se_mp)
  meanul95_mp = estimate_mp+(1.96*se_mp)

  #Now, smash all of those calculated values into one data frame (called 'dfCI').
  #You might get a warning about '...row names were found from a short variable...'
  #You can ignore it.
  dfCI_mp = data.frame(ll95_mp, ul95_mp, ll99_mp,
                       ul99_mp, se.seq_mp, estimate_mp, meanll95_mp, meanul95_mp)

  #Now we can actually make the funnel plot.
  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
    #Regression line for the FP asymmetry
    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
    #Add your data-points to the scatterplot
    geom_point(size = 2.5, colour="black") +
    #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + 
    # remove y label because it will be combined with the other funnel plot
    ylab('Hedge\'s g')+
    # give it a title
    ggtitle("Mispronunciation") +
    # make sure both plots have same scale
    # still xlim because we haven't flipped yet
    #coord_cartesian(xlim = c(0.5, 1))+
    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
    #to the lower and upper limits of your 95% CI region
    #And dashed lines corresponding to your 99% CI region
    #Add lines corresponding to 0 and estimate
    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
    #at the top of the figure once we swap the x- and y-axes...
    scale_x_reverse()+
    #Specify the range and interval for the tick-marks of the y-axis (Zr);
    #Choose values that work for you based on your data
    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
    #And now we flip the axes so that SE is on y- and Zr is on x-
    coord_flip()+
    #Finally, apply my APA-format theme (see previous).
    #You could, alternatively, specify theme_bw() instead.
    funnel_theme +
    theme(axis.title.y = element_blank())

  #Call the pretty funnel plot
  #fp_mp
#  ggsave("figures/FunnelPlot_misp.pdf")

@@

## Figure 1

```{r FunnelCombo, echo = FALSE}

  jpeg(filename = "figures/Figure_1_Funnel_Plots_Object_Identification.jpg", 
       width = 600, height = 400, units = "px")

  p <-   grid.arrange(fp_co, fp_mp, nrow = 1)
                      #top = textGrob("Object Identification", gp=gpar(fontsize=25)))
                      #top = "Figure 1. Funnel Plots")
  dev.off()

    grid.draw(p)

@@

```{r PcurveExport, echo = FALSE}

textfile_co = "p_curve_app/p_curve_co.txt"

# make sure the file is made new with our loop
if (file.exists(textfile_co)) {file.remove(textfile_co)}

for(line in 1:length(db_ET_correct$n_1)){
  if(!is.na(db_ET_correct[line,]$t)){
    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
    write(newline, file = textfile_co, append = TRUE)
    #cat("\n")
    #write(newline, file = textfile, append = TRUE)    
  }
}

textfile_mp = "p_curve_app/p_curve_mp.txt"

# make sure the file is made new with our loop
if (file.exists(textfile_mp)) {file.remove(textfile_mp)}

for(line in 1:length(db_ET_MP$n_1)){
  if(!is.na(db_ET_MP[line,]$t)){
    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
    write(newline, file = textfile_mp, append = TRUE)
    #cat("\n")
    #write(newline, file = textfile, append = TRUE)    
  }
}

@@

```{r ReadIn_pcurve_app,  echo = FALSE}

curdir <- getwd()

#Get the effect size data
source("scripts/p_curve_app_code.R")

# this gives the number of significant results
# the Z value
# and the significance
pcd_correct <- pcurve_app("p_curve_co.txt",paste0(curdir, "/p_curve_app"))

pcd_misp <- pcurve_app("p_curve_mp.txt",paste0(curdir, "/p_curve_app"))

@@

We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions. The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, p `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05. The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, p `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.

Taken together, these results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies. Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

## Meta-analysis

### Object Identification for Correct and Mispronounced Words

@@

#summary(rma_correct)
#kable(round(coef(summary(rma_correct)), 2))

sum_eff <- coef(summary(rma_correct))[1,]

@@

We first calculated the meta-analytic effect for object identification in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges’ *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research) and that it is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.

@@

#summary(rma_MP)

sum_eff <- coef(summary(rma_MP))[1,]

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size Hedges’ g was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated. But, as the p-curve indicated evidential value, we are confident in this result as well.

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, p `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, p `r psig(rma_MP$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.

### Mispronunciation Sensitivity Meta-analytic Effect

```{r MPEffect}

@@

#summary(rma_MPeffect)

#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)

#summary(rma_MPeffect_1)

sum_eff <- coef(summary(rma_MPeffect))[2,]

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we then compared the effect size Hedges’ *g* for correct pronunciations with mispronunciations, merging the two datasets. The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, p `r psig(rma_MPeffect$QMp)`.  Hedges’ *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the two type of responses were significantly different from one another (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.

### Object Recognition and Mispronunciation Sensitivity Modulated by Age

@@

#summary(rma_correct_age)
#kable(round(coef(summary(rma_correct_age)), 2))
#aov.type <- anova(rma_correct_age)

Csum_eff <- coef(summary(rma_correct_age))[2,]

@@

@@

#summary(rma_MP_age)
#aov.type <- anova(rma_MP_age)

Msum_eff <- coef(summary(rma_MP_age))[2,]

To evaluate the different predictions for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, p `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, p `r psig(rma_MP_age$QMp)`). The lack of a significant modulation indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

```{r MPEffect_age}

@@

# summary(rma_MPeffect_age)  
# 
# aov.type <- anova(rma_MPeffect_age)

sum_eff <- coef(summary(rma_MPeffect_age))[4,]

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant (QMQM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, p `r psig(rma_MPeffect_age$QMp)`). The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.

## Figure 2

```{r PlotMPEffect, echo = FALSE}

@@

# min(dat$mean_age_1/30.44)
# max(dat$mean_age_1/30.44)

@@

  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
       width = 700, height = 400, units = "px")

@@

### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary

```{r VocabularyData, echo = FALSE}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n(),
            papers = n_distinct(short_cite))

#kable(vocab_info)
